\sysfull

### 2018-08-07 paper/asplos19/implementation.tex
VMM -> PP
Implementation revised

%
\subsection{Task Coalescing}
%
% The coalescing algorithm starts with a random guess about the size of the coalescing task, in our implementation the target is initialized to four. It then refines its guess based on the number of the static-tasks being successfully executed.
%
\paragraph{Parameters.}
Equations (\ref{eq:eo}) and (\ref{eq:eg}) parametrize the behavior of the coalescing strategies in terms of $x$, $\rho$ and $\gamma$.
We experimented with a range of values, and then used the ones that yielded the best performance: $x = 1$ (for EO) and $\rho = \gamma = 1$ (for EG/WEG).

\paragraph{Weights for WEG.}
The effectiveness of the WEG hinges on correctly identifying the weight of each task, which WEG assumes is {\em statically} available. Profiling the time and energy cost of tasks in a program is a difficult, orthogonal problem~\cite{cleancut_2018,baghsorkhi_cgo_2018}. WEG could use the result of an arbitrarily sophisticated profiling procedure. To produce a concrete result in this paper, we give WEG access to a simple profile of task run time collected offline using a single fixed input. WEG stores the profile in a lookup table that maps a task's identifier to its weight, making the information available to \sys's scheduler at run time.

%
\subsection{Task Downscaling}
%
% \sys's task downscaling preserves forward progress by partially committing an
% ongoing, non-terminating task. 
%
\paragraph{Timer Strategy.}
After identifying a task as likely non-terminating, \sys must decide when during the task's execution to partially commit the task's state. \sys sets a timer at the start of the likely non-terminating task, initializing it to a very large value (e.g., an estimate of the maximum execution time using the device's energy buffer). If the timer expires before power fails, \sys partially commits, retaining  the timer value to use for future partial commits. If the timer does not expire before power fails, \sys halves the timer and tries again. The exponential decrease of the timer value converges rapidly to a usable one.
%
Partial commit relies on the existence of a hardware timer, which is a very
common feature in a typical MCU and consumes very little energy (i.e.,
$\approx$3\,$\mu$A/MHz~\cite{msp430datasheet}).

@@

% As described in Section~\ref{sec:memory_virtulaization}, \sys's memory
% virtualization scheme uses three buffers: a volatile \texttt{working} buffer, a
% non-volatile \texttt{\underline{private}}, and a non-volatile
% \texttt{\underline{shadow}} buffer. 
%
% The main memory \texttt{\underline{private}} holds the last committed copy of all 
% pages. 
%
% After reboot, the \texttt{working} buffer is empty. Execution fills 
% the \texttt{working} buffer with privatized pages as the program accesses them. 
%
% The \texttt{\underline{shadow}} buffer serves as an intermediate,
% non-volatile backing \texttt{\underline{private}} for dirty pages evicted from the space-constrained
% \texttt{working} buffer.

% To access a protected variable with either \texttt{RP}
% or \texttt{WP}, \sys searches for the variable in its \texttt{working} buffer first.
 % If the page is not, the VMM fetches it from non-volatile memory. 
%
\paragraph{Efficiency.}
\sys uses address-based page tagging to make finding a variable efficient.  The
upper bits of a variable's memory address identify its page, and the lower bits
denote the variable's offset in its page. The total number of pages in memory,
$P$, determines the number of tag bits, which is $\log_2 P$.
%
Furthermore, the VMM moves pages of data efficiently using hardware accelerated DMA support.

@@

\paragraph{Page Eviction.}
When a page in \texttt{working} has to be swapped out to make room for a newly requested one, an eviction policy has to be chosen.
While we opted for the simplicity of FIFO, any other replacement policy, such as Least Recently Used (LRU), could work in its place.

>>>>

%
\subsection{Task Coalescing}
%
% The coalescing algorithm starts with a random guess about the size of the coalescing task, in our implementation the target is initialized to four. It then refines its guess based on the number of the static-tasks being successfully executed.
%
\paragraph{Parameters.}
Equations (\ref{eq:eo}) and (\ref{eq:eg}) parametrize the behavior of the coalescing strategies in terms of $x$, $\rho$ and $\gamma$.
We experimented with a range of values, and then used the ones that yielded the best performance: $x = 1$ (for EO) and $\rho = \gamma = 1$ (for EG and WEG).

\paragraph{Weights for WEG.}
The effectiveness of the WEG hinges on correctly identifying the weight of each task, which WEG assumes is {\em statically} available. Profiling the time and energy cost of tasks in a program is a difficult, orthogonal problem~\cite{cleancut_2018,baghsorkhi_cgo_2018}. WEG could use the result of an arbitrarily sophisticated profiling procedure. To produce a concrete result in this paper, we give WEG access to a simple profile of task run time (collected offline) using a single fixed input. WEG stores the profile in a lookup table that maps a task's identifier to its weight, making the information available to \sys's scheduler at run time.

%
\subsection{Task Downscaling}
%
% \sys's task downscaling preserves forward progress by partially committing an
% ongoing, non-terminating task. 
%
\paragraph{Timer Strategy.}
After identifying a task as likely non-terminating, \sys must decide when during the task's execution to partially commit the task's state. \sys sets a timer at the start of the likely non-terminating task, initializing it to a very large value (e.g., an estimate of the maximum execution time using the device's energy buffer). If the timer expires before power fails, \sys partially commits, retaining  the timer value to use for future partial commits. If the timer does not expire before power fails, \sys halves the timer and tries again. The exponential decrease of the timer value converges rapidly to a usable one.
%
%Partial commit relies on the existence of a hardware timer, which is a very common feature in a typical MCU and consumes very little energy (i.e., $\approx$3\,$\mu$A/MHz~\cite{msp430datasheet}).

@@

\paragraph{Efficiency.}
\sys uses address-based page tagging to make finding a variable efficient.  The
upper bits of a variable's memory address identify its page, and the lower bits
denote the variable's offset in its page. The total number of pages in memory,
$P$, determines the number of tag bits, which is $\log_2 P$.
%
Furthermore, the PP moves pages of data efficiently using hardware accelerated DMA support.

@@

\paragraph{Page Eviction.}
When a page in \texttt{working} has to be swapped out to make room for a newly requested one, an eviction policy has to be chosen.
While we opted for the simplicity of FIFO, any other replacement policy, such as Least Recently Used, could work in its place.
